---
execute:
  echo: false
  message: false
  warning: false
---

```{r}
library(tidycensus)
library(tidyverse)
library(leaflet)
library(sf)
library(viridis)

x <- read_rds("fl_data.rds")
```


```{r}


# Define a color palette
pal <- colorNumeric(
  palette = "viridis",  # Use the "viridis" color scale
  domain = x$pct_bachelors  # Map to the pct_bachelors column
)

# Create the leaflet map
leaflet_map <- leaflet(x) %>%
  addTiles() %>%  # Add base map tiles
  addPolygons(
    color = ~pal(pct_bachelors),  # Color polygons based on pct_bachelors
    weight = 1,                   # Border thickness
    opacity = 1,                  # Border opacity
    fillOpacity = 0.7,            # Fill opacity
    popup = ~paste(               # Popup text when clicking on a tract
      "Tract: ", NAME, "<br>",
      "Population: ", B01003_001, "<br>",
      "% Bachelors: ", round(pct_bachelors, 2), "%"
    ),
    highlightOptions = highlightOptions(
      weight = 2,                 # Highlight border thickness
      color = "white",            # Highlight border color
      fillOpacity = 0.9,          # Highlight fill opacity
      bringToFront = TRUE         # Bring highlighted tract to front
    )
  ) %>%
  addLegend(
    position = "bottomright",     # Position of the legend
    pal = pal,                    # Color palette
    values = ~pct_bachelors,      # Values for the legend
    title = "% Bachelors"         # Legend title
  )

# Display the map
leaflet_map
```


This map shows a heat map of bachelor's degree attainment across the state of Florida. The map uses a color gradient from purple to yellow, where darker purple indicates lower percentages of bachelor's degree holders (0-10%) and lighter colors including greens and yellows represent higher percentages (up to 50%). There is significant variation across the state, with some clusters of higher educational attainment corresponding to major urban areas. The panhandle region and central Florida show generally darker purple coloring, suggesting lower rates of bachelor's degree attainment, while there are pockets of lighter colors, particularly along some coastal areas and what appear to be major metropolitan regions. 




